Meta RL analyses

### 2019-03-11 meta_RL_analyses.Rmd
Latest updates

result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   #"language", "language_simplified",
                   "language_noncompositional", "language_simplified", "language_meta_nontoggling",
                   "language_noncompositional_old", "language_simplified_random_holdout")

@@

```{r}
ggplot(avg_sweep_d %>%
         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_wrap(~ game_type)

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
language_d = load_d(results_dir, c("language_noncompositional_old", 
                                   #"language",  "language_nontoggling_random_holdout", 
                                   "language_simplified", "language_meta_nontoggling", "language_noncompositional",
                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
                               "language_meta_nontoggling", "language_noncompositional"
                               ), num_runs, "new_language_meta_true_losses")

>>>>

result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "meta_batch_64", "meta_batch_128", "meta_batch_256",
                   #"language", "language_simplified",
                   "language_noncompositional", "language_simplified", "language_meta_nontoggling",
                   "language_noncompositional_old", "language_simplified_random_holdout",
                   "language_mb_128_ne_15","language_mb_128_ne_20")

@@

```{r}
ggplot(avg_sweep_d %>%
         filter(run_type == "basic" | run_type == "meta_batch_256"), aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "meta_batch_256", "meta_batch_128", "meta_batch_64", "language_mb_128_ne_15"),
                              size < 200), aes(x=size, color=named_run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
language_d = load_d(results_dir, c("language_noncompositional_old", 
                                   #"language",  "language_nontoggling_random_holdout", 
                                   "language_simplified", "language_meta_nontoggling", "language_noncompositional",
                                   "language_mb_128_ne_15","language_mb_128_ne_20",
                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
                               "language_mb_128_ne_15","language_mb_128_ne_20",
                               "language_meta_nontoggling", "language_noncompositional"
                               ), num_runs, "new_language_meta_true_losses")
